\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{parskip}

\pagestyle{empty}
\titleformat{\section}{\large\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{Shatham Anileshwar}} \\
    \vspace{4pt}
    \small
    \href{mailto:anileshwar7@gmail.com}{anileshwar07@gmail.com} \quad | \quad +91-93470-49594 \quad | \quad
    \href{https://github.com/anileshwar12}{github.com/anileshwar12} \quad | \quad
    \href{https://www.linkedin.com/in/anileshwar/}{linkedin.com/in/anileshwar} \\
\normalsize
\end{center}



\vspace{-1em}
\section*{Profile}
App Lead at Codeholics Club with experience building impactful mobile apps. Currently studying AI/ML with a focus on core algorithms. Actively solving DSA problems to strengthen problem-solving skills. Passionate about Android development and leading app projects from idea to execution.

\section*{Experience \& Leadership}

\textbf{App Development – Codeholics Club} \hfill \textit{Feb 2025 – Present} \\
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Leading app development initiatives in the college's coding club.
    \item Mentoring juniors and contributing to building tech awareness via projects and workshops.
    \item Working to bridge the gap between college students and government incubators.
\end{itemize}

\textbf{Co-Founder – Mini Brain (SaaS in Development)} \hfill \textit{Apr 2025 – Present} \\
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Leading development of an offline memory-integrated AI assistant for user queries.
    \item Collaborating with a 3-member founding team on architecture, roadmap, and features.
    \item Designing Android app UI with Jetpack Compose and Kotlin for local ML inference and RoomDB search.

\end{itemize}

\section*{Skills}

\begin{multicols}{2}
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item \textbf{Languages:} Java, C, C++, Python, Kotlin
    \item \textbf{Development:} Android Studio, Jetpack Compose, Unity, Firebase, Supabase
    \item \textbf{Tools/Platforms:} Git, GitHub, Google Colab, Linux
    \item \textbf{API Integration:} REST APIs

\end{itemize}
\end{multicols}



\section*{Projects}

\textbf{Doctor Appointment Booking App} \hfill \textit{Mar 2025 – Present} \\
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Built an Android app using Jetpack Compose and Kotlin for streamlined doctor appointment scheduling.
    \item Integrated Firebase for secure user authentication and Firestore for storing user profiles and bookings.
    \item Features include dynamic ticket generation with QR codes, profile management, location-based search, and a smooth UI with category-based navigation.
    \item Designed user dashboard with real-time appointment tracking and medicine records.
\end{itemize}

\textbf{Weather App} \hfill \textit{Dec 2024} \\
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Developed an Android app using Java that fetches real-time weather data for any city.
    \item Integrated OpenWeatherMap API and designed a clean, user-friendly UI.
\end{itemize}

\textbf{Expense Tracker} \hfill \textit{Apr 2024} \\
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Created an Android app with Firebase backend for authentication and expense tracking.
    \item Implemented real-time updates using Firebase Realtime Database.
\end{itemize}



\section*{Education}

\textbf{CMR Technical Campus, Hyderabad} \hfill \textit{Sep 2023 – Present} \\
B.Tech in Computer Science \\
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Specialized in Android app development; currently exploring AI/ML.
    \item Built real-world apps and games while participating in coding competitions.
\end{itemize}

\textbf{RGUKT, Basar} \hfill \textit{Nov 2021 – Jul 2023} \\
Intermediate Education \\
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Learned Python for automation and problem-solving.
    \item Gained hands-on experience in Linux terminal, scripting, and file system navigation.
\end{itemize}



\section*{Achievements}

\textbf{Smart India Hackathon (SIH) – College Level} \hfill \textit{2024} \\
Secured 7\textsuperscript{th} place for developing a Farmers' Shopping Application.

\section*{Languages Known}

Telugu (Native), English (Fluent), Hindi (Conversational)

\end{document}
